---
title: "WINDMLPR"
author: "Connor Simpson"
date: "12/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
crossvalidtest <- function(ts,exog,k,h){
  pred = data.frame(ts)
  tru = data.frame(ts)
  testa = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  traina = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  arsq=0
  WMAPE=0
  rmse=0
  reler=0
  v = as.integer(length(ts)/(2*k))
  size = 2*v
  error = rep(NA,(k-1))
  for (i in (0:(k-1))){
    if (i == 0){z = 0}
    else{z=1}
      if (i == k-1){z2 = 0}
    else{z2=1}
    test = rep(NA,length(ts))
    testx = data.frame(exog)
    for (bb in (1:length(exog))){
      testx[bb] = c(rep(NA,length(exog[,bb])))
    }
    train = ts
    trainx = exog
    test[((size)*i+1):((size)*i+size)] = ts[((size)*i+1):((size)*i+size)]
    for (m in (1:length(testx))){
      testx[((size)*i+1):((size)*i+size),m] = exog[((size)*i+1):((size)*i+size),m]
    }
    train[((size)*i+1-h*z):((size)*i+size+h*z2)] = NA
    for (b in (1:length(trainx))){
      trainx[((size)*i+1-h*z):((size)*i+size+h*z2),b] = NA
    }
    #mod = Arima(train,order = order,xreg = trainx,include.constant = F)
    #modt = Arima(test,model = mod,xreg=testx,include.constant = F)
    #error[i+1] = accuracy(modt)[2]
    #coefnum = sum(order)
    #pred1 = modt$fitted
    #tru1 = test
    #print(length(tsori))
    #print(length(pred1))
    #print(length(tru1))
    #pred = antidiff(tsori,pred1)
    #tru = antidiff(tsori,tru1)
    
    
    
    #plot.ts(pred,col=2)
    #plot.ts(tru,col=4)
    #plot.ts(tru-pred)
    #print(sum(abs(tru),na.rm=T))
    #print(sum(abs(tru-pred),na.rm=T))
    #arsq[i+1] = adjr(pred,tru,coefnum)
    #WMAPE[i+1] = WMAPE(pred,tru)
    #rmse[i+1] = rootMSE(tru,pred)
    #bench = tru[-length(tru)]
    #trub = tru[-1]
    #predb = pred[-1]
    #reler[i+1] = reler(predb,trub,bench)
    #print(arsq)
    #pred[i+1] = modt$fitted
    #tru[i+1] = test
    testa[,i+1]=test
    #traina[,i+1] = train
    
    
  }
  #return(data.frame(arsq,WMAPE,rmse,reler))
  #return(data.frame(pred,tru))
  return(testa)
}
```

```{r}
crossvalidtrain <- function(ts,exog,k,h){
  pred = data.frame(ts)
  tru = data.frame(ts)
  testa = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  traina = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  arsq=0
  WMAPE=0
  rmse=0
  reler=0
  v = as.integer(length(ts)/(2*k))
  size = 2*v
  error = rep(NA,(k-1))
  for (i in (0:(k-1))){
    if (i == 0){z = 0}
    else{z=1}
      if (i == k-1){z2 = 0}
    else{z2=1}
    test = rep(NA,length(ts))
    testx = data.frame(exog)
    for (bb in (1:length(exog))){
      testx[bb] = c(rep(NA,length(exog[,bb])))
    }
    train = ts
    trainx = exog
    test[((size)*i+1):((size)*i+size)] = ts[((size)*i+1):((size)*i+size)]
    for (m in (1:length(testx))){
      testx[((size)*i+1):((size)*i+size),m] = exog[((size)*i+1):((size)*i+size),m]
    }
    train[((size)*i+1-h*z):((size)*i+size+h*z2)] = NA
    for (b in (1:length(trainx))){
      trainx[((size)*i+1-h*z):((size)*i+size+h*z2),b] = NA
    }
    #mod = Arima(train,order = order,xreg = trainx,include.constant = F)
    #modt = Arima(test,model = mod,xreg=testx,include.constant = F)
    #error[i+1] = accuracy(modt)[2]
    #coefnum = sum(order)
    #pred1 = modt$fitted
    #tru1 = test
    #print(length(tsori))
    #print(length(pred1))
    #print(length(tru1))
    #pred = antidiff(tsori,pred1)
    #tru = antidiff(tsori,tru1)
    
    
    
    #plot.ts(pred,col=2)
    #plot.ts(tru,col=4)
    #plot.ts(tru-pred)
    #print(sum(abs(tru),na.rm=T))
    #print(sum(abs(tru-pred),na.rm=T))
    #arsq[i+1] = adjr(pred,tru,coefnum)
    #WMAPE[i+1] = WMAPE(pred,tru)
    #rmse[i+1] = rootMSE(tru,pred)
    #bench = tru[-length(tru)]
    #trub = tru[-1]
    #predb = pred[-1]
    #reler[i+1] = reler(predb,trub,bench)
    #print(arsq)
    #pred[i+1] = modt$fitted
    #tru[i+1] = test
    testa[,i+1]=test
    traina[,i+1] = train
    
    
  }
  #return(data.frame(arsq,WMAPE,rmse,reler))
  #return(data.frame(pred,tru))
  return(traina)
}
```


```{r}
datawind = read.csv("BiochemWind.csv")
```

```{r}
TEMP1 = datawind[,2]
TEMP2 = datawind[,3]
CNDC1 = datawind[,4]
CNDC2 =datawind[,5]
TURB1 = datawind[,8]
TURB2 = datawind[,9]
PAR1 = datawind[,10]
PAR2= datawind[,11]
CPHL1 = datawind[,12]
CPHL2= datawind[,13]
WIND = datawind[,18]
```

```{r}
TEMP = data.frame(TEMP1,TEMP2)
CNDC = data.frame(CNDC1,CNDC2)
TURB = data.frame(TURB1,TURB2)
PAR = data.frame(PAR1,PAR2)
CPHL = data.frame(CPHL1,CPHL2)
```

```{r}
WINDmax = max(WIND,na.rm = T)
WINDmin = min(WIND,na.rm = T)
WINDNorm = (WIND - WINDmin)/(WINDmax-WINDmin)
```


```{r}
TEMP = (TEMP-min(TEMP,na.rm=T))/(max(TEMP,na.rm=T)-min(TEMP,na.rm=T))
TURB = (TURB-min(TURB,na.rm=T))/(max(TURB,na.rm=T)-min(TURB,na.rm=T))
PAR = (PAR-min(PAR,na.rm=T))/(max(PAR,na.rm=T)-min(PAR,na.rm=T))
CPHL = (CPHL-min(CPHL,na.rm=T))/(max(CPHL,na.rm=T)-min(CPHL,na.rm=T))
CNDC = (CNDC-min(CNDC,na.rm=T))/(max(CNDC,na.rm=T)-min(CNDC,na.rm=T))
```








```{r}
WINDTestdata = crossvalidtest(WINDNorm,data.frame(WINDNorm),5,100)
plot.ts(WINDTestdata)
```

```{r}
write.csv(WINDTestdata,file = "WINDTestdata.csv")
```

```{r}
WINDTraindata = crossvalidtrain(WINDNorm,data.frame(WINDNorm),5,100)
plot.ts(WINDTraindata[,2])
lines(WINDTestdata[,2],col=2)
```

```{r}
write.csv(WINDTraindata,file = "WINDTraindata.csv")
```


```{r}
crossvalidtrainx <- function(ts,exog,k,h){
  pred = data.frame(ts)
  tru = data.frame(ts)
  testa = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  traina = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  trainax = data.frame(as.matrix(exog))
  arsq=0
  WMAPE=0
  rmse=0
  reler=0
  v = as.integer(length(ts)/(2*k))
  size = 2*v
  error = rep(NA,(k-1))
  for (i in (0:(k-1))){
    if (i == 0){z = 0}
    else{z=1}
      if (i == k-1){z2 = 0}
    else{z2=1}
    test = rep(NA,length(ts))
    testx = data.frame(exog)
    for (bb in (1:length(exog))){
      testx[bb] = c(rep(NA,length(exog[,bb])))
    }
    train = ts
    trainx = exog
    test[((size)*i+1):((size)*i+size)] = ts[((size)*i+1):((size)*i+size)]
    for (m in (1:length(testx))){
      testx[((size)*i+1):((size)*i+size),m] = exog[((size)*i+1):((size)*i+size),m]
    }
    train[((size)*i+1-h*z):((size)*i+size+h*z2)] = NA
    for (b in (1:length(trainx))){
      trainx[((size)*i+1-h*z):((size)*i+size+h*z2),b] = NA
    }
    #mod = Arima(train,order = order,xreg = trainx,include.constant = F)
    #modt = Arima(test,model = mod,xreg=testx,include.constant = F)
    #error[i+1] = accuracy(modt)[2]
    #coefnum = sum(order)
    #pred1 = modt$fitted
    #tru1 = test
    #print(length(tsori))
    #print(length(pred1))
    #print(length(tru1))
    #pred = antidiff(tsori,pred1)
    #tru = antidiff(tsori,tru1)
    
    
    
    #plot.ts(pred,col=2)
    #plot.ts(tru,col=4)
    #plot.ts(tru-pred)
    #print(sum(abs(tru),na.rm=T))
    #print(sum(abs(tru-pred),na.rm=T))
    #arsq[i+1] = adjr(pred,tru,coefnum)
    #WMAPE[i+1] = WMAPE(pred,tru)
    #rmse[i+1] = rootMSE(tru,pred)
    #bench = tru[-length(tru)]
    #trub = tru[-1]
    #predb = pred[-1]
    #reler[i+1] = reler(predb,trub,bench)
    #print(arsq)
    #pred[i+1] = modt$fitted
    #tru[i+1] = test
    testa[,i+1]=test
    traina[,i+1] = train
    trainax[,i+1] = as.matrix(trainx)
    
  }
  #return(data.frame(arsq,WMAPE,rmse,reler))
  #return(data.frame(pred,tru))
  return(trainax)
}
```


```{r}
crossvalidtestx <- function(ts,exog,k,h){
  pred = data.frame(ts)
  tru = data.frame(ts)
  testa = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  traina = data.frame(matrix(data=NA,nrow=length(ts),ncol = k))
  trainax = data.frame(as.matrix(exog))
  testax = data.frame(as.matrix(exog))
  arsq=0
  WMAPE=0
  rmse=0
  reler=0
  v = as.integer(length(ts)/(2*k))
  size = 2*v
  error = rep(NA,(k-1))
  for (i in (0:(k-1))){
    if (i == 0){z = 0}
    else{z=1}
      if (i == k-1){z2 = 0}
    else{z2=1}
    test = rep(NA,length(ts))
    testx = data.frame(exog)
    for (bb in (1:length(exog))){
      testx[bb] = c(rep(NA,length(exog[,bb])))
    }
    train = ts
    trainx = exog
    test[((size)*i+1):((size)*i+size)] = ts[((size)*i+1):((size)*i+size)]
    for (m in (1:length(testx))){
      testx[((size)*i+1):((size)*i+size),m] = exog[((size)*i+1):((size)*i+size),m]
    }
    train[((size)*i+1-h*z):((size)*i+size+h*z2)] = NA
    for (b in (1:length(trainx))){
      trainx[((size)*i+1-h*z):((size)*i+size+h*z2),b] = NA
    }
    #mod = Arima(train,order = order,xreg = trainx,include.constant = F)
    #modt = Arima(test,model = mod,xreg=testx,include.constant = F)
    #error[i+1] = accuracy(modt)[2]
    #coefnum = sum(order)
    #pred1 = modt$fitted
    #tru1 = test
    #print(length(tsori))
    #print(length(pred1))
    #print(length(tru1))
    #pred = antidiff(tsori,pred1)
    #tru = antidiff(tsori,tru1)
    
    
    
    #plot.ts(pred,col=2)
    #plot.ts(tru,col=4)
    #plot.ts(tru-pred)
    #print(sum(abs(tru),na.rm=T))
    #print(sum(abs(tru-pred),na.rm=T))
    #arsq[i+1] = adjr(pred,tru,coefnum)
    #WMAPE[i+1] = WMAPE(pred,tru)
    #rmse[i+1] = rootMSE(tru,pred)
    #bench = tru[-length(tru)]
    #trub = tru[-1]
    #predb = pred[-1]
    #reler[i+1] = reler(predb,trub,bench)
    #print(arsq)
    #pred[i+1] = modt$fitted
    #tru[i+1] = test
    testa[,i+1]=test
    traina[,i+1] = train
    trainax[,i+1] = as.matrix(trainx)
    testax[,i+1] = as.matrix(testx)
  }
  #return(data.frame(arsq,WMAPE,rmse,reler))
  #return(data.frame(pred,tru))
  return(testax)
}
```

```{r}
WINDTraindataxTEMP = crossvalidtrainx(WIND,data.frame(TEMP),5,100)
plot.ts(WINDTraindataxTEMP[,1])
```

```{r}
WINDTraindataxCNDC = crossvalidtrainx(WIND,data.frame(CNDC),5,100)
plot.ts(WINDTraindataxCNDC[,1])
```

```{r}
WINDTraindataxPAR = crossvalidtrainx(WIND,data.frame(PAR),5,100)
plot.ts(WINDTraindataxPAR[,1])
```


```{r}
WINDTraindataxTURB = crossvalidtrainx(WIND,data.frame(TURB),5,100)
plot.ts(WINDTraindataxTURB[,1])
```

```{r}
WINDTraindataxCPHL = crossvalidtrainx(WIND,data.frame(CPHL),5,100)
plot.ts(WINDTraindataxCPHL[,1])
```





```{r}
WINDtestdataxTURB = crossvalidtestx(WIND,data.frame(TURB),5,100)
plot.ts(WINDtestdataxTURB[,1])
```

```{r}
WINDtestdataxPAR = crossvalidtestx(WIND,data.frame(PAR),5,100)
plot.ts(WINDtestdataxPAR[,1])
```

```{r}
WINDtestdataxCPHL = crossvalidtestx(WIND,data.frame(CPHL),5,100)
plot.ts(WINDtestdataxCPHL[,1])
```

```{r}
WINDtestdataxTEMP = crossvalidtestx(WIND,data.frame(TEMP),5,100)
plot.ts(WINDtestdataxTEMP[,1])
```
```{r}
WINDtestdataxCNDC = crossvalidtestx(WIND,data.frame(CNDC),5,100)
plot.ts(WINDtestdataxCNDC[,1])
```



```{r}
write.csv(WINDTraindataxTEMP,file = "WINDTraindataxTEMP.csv")
write.csv(WINDTraindataxPAR,file = "WINDTraindataxPAR.csv")
write.csv(WINDTraindataxTURB,file = "WINDTraindataxTURB.csv")
write.csv(WINDTraindataxCPHL,file = "WINDTraindataxCPHL.csv")
write.csv(WINDTraindataxCNDC,file = "WINDTraindataxCNDC.csv")

write.csv(WINDtestdataxTURB,file = "WINDtestdataxTURB.csv")
write.csv(WINDtestdataxPAR,file = "WINDtestdataxPAR.csv")
write.csv(WINDtestdataxCPHL,file = "WINDtestdataxCPHL.csv")
write.csv(WINDtestdataxTEMP,file = "WINDtestdataxTEMP.csv")
write.csv(WINDtestdataxCNDC,file = "WINDtestdataxCNDC.csv")
```







WMAPE
REMOVE ABS ON SUM(TRU)
```{r}
WMAPE <- function(pred,tru){
  WMAPE = sum((sum(abs(pred-tru)/tru,na.rm = T)/sum(tru,na.rm = T))*tru,na.rm=T)/length(na.remove(tru))
  return(WMAPE)
}
```


reler
```{r}
reler <- function(pred,tru,bench){
  reler = sum(abs(tru-pred),na.rm = T)/sum(abs(tru-bench),na.rm = T)
  return(reler)
}
```

rsq 
```{r}
rsq <- function(pred,tru){
  SSE = sum((tru-pred)^2,na.rm = T)
  SS = sum((tru-mean(na.omit(tru)))^2,na.rm = T)
  rsq = 1- SSE/SS
  return(rsq)
}
```


adjr
```{r}
adjr <- function(pred,tru,coefnum){
  rs = rsq(pred,tru)
  n = length(pred)
  adjr = 1-(1-rs)*(n-1)/(n-coefnum-1)
  return(adjr)
}
```

rmse
```{r}
rootMSE = function(pred,tru){
  return(sqrt(mean((pred-tru)^2,na.rm = T)))
}
```


```{r}
pred0 = read.csv("WIND0.csv")[,2]*(WINDmax-WINDmin) + WINDmin
pred1 = read.csv("WIND1.csv")[,2]*(WINDmax-WINDmin) + WINDmin
pred2 = read.csv("WIND2.csv")[,2]*(WINDmax-WINDmin) + WINDmin
pred3 = read.csv("WIND3.csv")[,2]*(WINDmax-WINDmin) + WINDmin
pred4 = read.csv("WIND4.csv")[,2]*(WINDmax-WINDmin) + WINDmin

tru0 = read.csv("WIND0tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
tru1 = read.csv("WIND1tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
tru2 = read.csv("WIND2tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
tru3 = read.csv("WIND3tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
tru4 = read.csv("WIND4tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
```

```{r}
plot.ts(pred0)
lines(tru0,col=2)
plot.ts(pred1)
lines(tru1,col=2)
plot.ts(pred2)
lines(tru2,col=2)
plot.ts(pred3)
lines(tru3,col=2)
plot.ts(pred4)
lines(tru4,col=2)
```

```{r}
adjr0 = adjr(pred0,tru0,10)
adjr1 = adjr(pred1,tru1,10)
adjr2 = adjr(pred2,tru2,10)
adjr3 = adjr(pred3,tru3,10)
adjr4 = adjr(pred4,tru4,10)
mean(c(adjr0,adjr1,adjr2,adjr3,adjr4))
```

```{r}
rootMSE0 = rootMSE(pred0,tru0)
rootMSE1 = rootMSE(pred1,tru1)
rootMSE2 = rootMSE(pred2,tru2)
rootMSE3 = rootMSE(pred3,tru3)
rootMSE4 = rootMSE(pred4,tru4)
mean(c(rootMSE0,rootMSE1,rootMSE2,rootMSE3,rootMSE4))
```

```{r}
WMAPE0 = WMAPE(pred0,tru0)
WMAPE1 = WMAPE(pred1,tru1)
WMAPE2 = WMAPE(pred2,tru2)
WMAPE3 = WMAPE(pred3,tru3)
WMAPE4 = WMAPE(pred4,tru4)
mean(c(WMAPE0,WMAPE1,WMAPE2,WMAPE3,WMAPE4))
```



```{r}
predCNDC0 = read.csv("WINDCNDC0.csv")[,2]*(WINDmax-WINDmin) + WINDmin
predCNDC1 = read.csv("WINDCNDC1.csv")[,2]*(WINDmax-WINDmin) + WINDmin
predCNDC2 = read.csv("WINDCNDC2.csv")[,2]*(WINDmax-WINDmin) + WINDmin
predCNDC3 = read.csv("WINDCNDC3.csv")[,2]*(WINDmax-WINDmin) + WINDmin
predCNDC4 = read.csv("WINDCNDC4.csv")[,2]*(WINDmax-WINDmin) + WINDmin

truCNDC0 = read.csv("WINDCNDC0tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
truCNDC1 = read.csv("WINDCNDC1tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
truCNDC2 = read.csv("WINDCNDC2tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
truCNDC3 = read.csv("WINDCNDC3tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
truCNDC4 = read.csv("WINDCNDC4tru.csv")[,2]*(WINDmax-WINDmin) + WINDmin
```

```{r}
plot.ts(predCNDC0)
lines(truCNDC0,col=2)
plot.ts(predCNDC1)
lines(truCNDC1,col=2)
plot.ts(predCNDC2)
lines(truCNDC2,col=2)
plot.ts(predCNDC3)
lines(truCNDC3,col=2)
plot.ts(predCNDC4)
lines(truCNDC4,col=2)
```

```{r}
adjr0 = adjr(predCNDC0,truCNDC0,10)
adjr1 = adjr(predCNDC1,truCNDC1,10)
adjr2 = adjr(predCNDC2,truCNDC2,10)
adjr3 = adjr(predCNDC3,truCNDC3,10)
adjr4 = adjr(predCNDC4,truCNDC4,10)
mean(c(adjr0,adjr1,adjr2,adjr3,adjr4))
```

```{r}
rootMSE0 = rootMSE(predCNDC0,truCNDC0)
rootMSE1 = rootMSE(predCNDC1,truCNDC1)
rootMSE2 = rootMSE(predCNDC2,truCNDC2)
rootMSE3 = rootMSE(predCNDC3,truCNDC3)
rootMSE4 = rootMSE(predCNDC4,truCNDC4)
mean(c(rootMSE0,rootMSE1,rootMSE2,rootMSE3,rootMSE4))
```

```{r}
WMAPE0 = WMAPE(predCNDC0,tru0)
WMAPE1 = WMAPE(predCNDC1,tru1)
WMAPE2 = WMAPE(predCNDC2,tru2)
WMAPE3 = WMAPE(predCNDC3,tru3)
WMAPE4 = WMAPE(predCNDC4,tru4)
mean(c(WMAPE0,WMAPE1,WMAPE2,WMAPE3,WMAPE4))
```


import numpy as np
import pandas as pd
from sklearn.neural_network import MLPRegressor
import matplotlib.pyplot as plt


CNDCTestdata = pd.read_csv("CNDCTestdata.csv")
CNDCTraindata = pd.read_csv("CNDCTraindata.csv")

CNDCTraindataxCNDC = pd.read_csv("CNDCTraindataxCNDC.csv")
CNDCTraindataxPAR = pd.read_csv("CNDCTraindataxPAR.csv")
CNDCTraindataxTURB = pd.read_csv("CNDCTraindataxTURB.csv")
CNDCTraindataxCPHL = pd.read_csv("CNDCTraindataxCPHL.csv")
CNDCTraindataxTEMP = pd.read_csv("CNDCTraindataxTEMP.csv")


CNDCtestdataxTURB = pd.read_csv("CNDCtestdataxTURB.csv")
CNDCtestdataxPAR = pd.read_csv("CNDCtestdataxPAR.csv")
CNDCtestdataxCNDC = pd.read_csv("CNDCtestdataxCNDC.csv")
CNDCtestdataxCPHL = pd.read_csv("CNDCtestdataxCPHL.csv")
CNDCtestdataxTEMP = pd.read_csv("CNDCtestdataxTEMP.csv")
#################################################

CNDCTestdata = CNDCTestdata.iloc[:,1:]
CNDCTraindata = CNDCTraindata.iloc[:,1:]

CNDCTraindataxCNDC = CNDCTraindataxCNDC.iloc[:,1:]
CNDCTraindataxPAR = CNDCTraindataxPAR.iloc[:,1:]
CNDCTraindataxTURB = CNDCTraindataxTURB.iloc[:,1:]
CNDCTraindataxCPHL = CNDCTraindataxCPHL.iloc[:,1:]
CNDCTraindataxTEMP = CNDCTraindataxTEMP.iloc[:,1:]

CNDCtestdataxTURB = CNDCtestdataxTURB.iloc[:,1:]
CNDCtestdataxPAR = CNDCtestdataxPAR.iloc[:,1:]
CNDCtestdataxCNDC = CNDCtestdataxCNDC.iloc[:,1:]
CNDCtestdataxCPHL = CNDCtestdataxCPHL.iloc[:,1:]
CNDCtestdataxTEMP = CNDCtestdataxTEMP.iloc[:,1:]

#################################################




CNDCxCNDCtrain = pd.concat([CNDCTraindata,CNDCTraindataxCNDC,CNDCTraindataxPAR,CNDCTraindataxTURB,CNDCTraindataxCPHL,CNDCTraindataxTEMP],axis=1)
CNDCxCNDCtest = pd.concat([CNDCTestdata,CNDCtestdataxCNDC,CNDCtestdataxPAR,CNDCtestdataxTURB,CNDCtestdataxCPHL,CNDCtestdataxTEMP],axis=1)
for i in range(0,5):
    CNDCdata = CNDCxCNDCtrain.iloc[:,[i,i*2+5,i*2+6,i*2+15,i*2+16,i*2+25,i*2+26,i*2+35,i*2+36,i*2+45,i*2+46]]
    CNDCdata = CNDCdata.dropna()
    CNDCtrain = CNDCdata.iloc[:,0]
    CNDCtrainx = CNDCdata.iloc[:,[1,2,3,4,5,6,7,8,9,10]]
    
    regressorCNDCxCNDC = MLPRegressor()
    regressorCNDCxCNDC.fit(CNDCtrainx,CNDCtrain)
    
    CNDCdatatest = CNDCxCNDCtest.iloc[:,[i,i*2+5,i*2+6,i*2+15,i*2+16,i*2+25,i*2+26,i*2+35,i*2+36,i*2+45,i*2+46]]
    CNDCdatatest = CNDCdatatest.dropna()
    CNDCdatatest = CNDCdatatest.reset_index().iloc[:,1:]
    globals()['CNDCtest'+str(i)]  = CNDCdatatest.iloc[:,0]
    CNDCtest = CNDCdatatest.iloc[:,[1,2,3,4,5,6,7,8,9,10]]
    globals()['pred'+str(i)] = regressorCNDCxCNDC.predict(CNDCtest)


pred0 = pd.DataFrame(pred0)
pred0.to_csv("CNDC0.csv")
pred1 = pd.DataFrame(pred1)
pred1.to_csv("CNDC1.csv")
pred2 = pd.DataFrame(pred2)
pred2.to_csv("CNDC2.csv")
pred3 = pd.DataFrame(pred3)
pred3.to_csv("CNDC3.csv")
pred4 = pd.DataFrame(pred4)
pred4.to_csv("CNDC4.csv")

CNDCtest0 = pd.DataFrame(CNDCtest0)
CNDCtest0.to_csv("CNDC0tru.csv")
CNDCtest1 = pd.DataFrame(CNDCtest1)
CNDCtest1.to_csv("CNDC1tru.csv")
CNDCtest2 = pd.DataFrame(CNDCtest2)
CNDCtest2.to_csv("CNDC2tru.csv")
CNDCtest3 = pd.DataFrame(CNDCtest3)
CNDCtest3.to_csv("CNDC3tru.csv")
CNDCtest4 = pd.DataFrame(CNDCtest4)
CNDCtest4.to_csv("CNDC4tru.csv")


CNDCxCNDCtrain = pd.concat([CNDCTraindata,CNDCTraindataxCNDC],axis=1)
CNDCxCNDCtest = pd.concat([CNDCTestdata,CNDCtestdataxCNDC],axis=1)
for i in range(0,5):
    CNDCdata = CNDCxCNDCtrain.iloc[:,[i,i*2+5,i*2+6]]
    CNDCdata = CNDCdata.dropna()
    CNDCtrain = CNDCdata.iloc[:,0]
    CNDCtrainx = CNDCdata.iloc[:,[1,2]]
    
    regressorCNDCxCNDC = MLPRegressor()
    regressorCNDCxCNDC.fit(CNDCtrainx,CNDCtrain)
    
    CNDCdatatest = CNDCxCNDCtest.iloc[:,[i,i*2+5,i*2+6]]
    CNDCdatatest = CNDCdatatest.dropna()
    CNDCdatatest = CNDCdatatest.reset_index().iloc[:,1:]
    globals()['CNDCtestTEMP'+str(i)]  = CNDCdatatest.iloc[:,0]
    CNDCtest = CNDCdatatest.iloc[:,[1,2]]
    globals()['predTEMP'+str(i)] = regressorCNDCxCNDC.predict(CNDCtest)


pred0 = pd.DataFrame(predTEMP0)
pred0.to_csv("CNDCTEMP0.csv")
pred1 = pd.DataFrame(predTEMP1)
pred1.to_csv("CNDCTEMP1.csv")
pred2 = pd.DataFrame(predTEMP2)
pred2.to_csv("CNDCTEMP2.csv")
pred3 = pd.DataFrame(predTEMP3)
pred3.to_csv("CNDCTEMP3.csv")
pred4 = pd.DataFrame(predTEMP4)
pred4.to_csv("CNDCTEMP4.csv")

CNDCtest0 = pd.DataFrame(CNDCtestTEMP0)
CNDCtest0.to_csv("CNDCTEMP0tru.csv")
CNDCtest1 = pd.DataFrame(CNDCtestTEMP1)
CNDCtest1.to_csv("CNDCTEMP1tru.csv")
CNDCtest2 = pd.DataFrame(CNDCtestTEMP2)
CNDCtest2.to_csv("CNDCTEMP2tru.csv")
CNDCtest3 = pd.DataFrame(CNDCtestTEMP3)
CNDCtest3.to_csv("CNDCTEMP3tru.csv")
CNDCtest4 = pd.DataFrame(CNDCtestTEMP4)
CNDCtest4.to_csv("CNDCTEMP4tru.csv")